\Large Analyzing the Supreme Court Citation Network

### 2017-12-29 Tex/paper.tex
revising notation

Let $c_{ij} \in \{0,1\}$ be a binary indicator of whether case $i$ cites $j$. Furthermore, let
$$\mathcal{C}_t=\{c(t)\in \{0,1\}^{N_t}: c_{ij}(t)\in \{0,1\} \}$$ 
be the set of all possible citation combinations for opinions issued in term $t$, where $c_{ij}(t)$ is a binary indicator of whether case $i$ cites case $j$, and case $i$ is decided at time $t$. Note that the cardinality of $\mathcal{C}_t$ increases exponentially for every newly added case.\\ The probability function of the c-TERGM  is defined as
\begin{equation}
P_{\theta}(c(t)~|~c(t-))=\cfrac{\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}{\sum_{z(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(z(t)~|~c(t-)\big)\big)}
\label{ercm}
\end{equation}
where $c(t-)$ is a matrix that indicates the citations among cases decided before time $t$, $\theta \in \mathbb{R}^q$ is a $q$-dimensional vector of parameters,  $h: \mathcal{C}_t \to \mathbb{R}^q ~, ~ \c(t) \to (h_1(c(t)), \dots , h_q(c(t)))^T$ is a q-dimensional vector of different statistics and $\kappa(\theta) := \sum_{z(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(z(t)~|~c(t-)\big))$ is a normalization constant that ensures that (\ref{ercm}) defines a probability function on $\mathcal{C}_t$.\\[0.3cm]

% Network Statistics
The generative process of a model are informed by
the decision regarding which network statistics $h(\cdot)$ are incorporated. We include the following statistics for the Supreme Court citation network:
$$h_{edges}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{i=1}^Nc_i(t)$$
the number of citations made at time $t$. 
$$h_{outstar}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{j<i}^Nc_i(t)\cdot c_j(t) \cdot \sqrt{\dfrac{(t-a)(t-a-b)}{t^2}}$$
the number of weighted outstars occuring at time $t$. We argue that it should be more likely to cite more recent cases than cases that have been decided further in the past. For the weight 
$$w(a,b):= \sqrt{\dfrac{(t-a)(t-a-b)}{t^2}}$$
we define $a$ and $b$ as the elapsed time since case $i$ and $j$ have been introduced to the network.
$$h_{triangle}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{j<i}^Nc_i(t)\cdot c_j(t) \cdot
c_j(t_{-i}) \cdot w(a,b)$$
where $c_j(t_{-i})$ indicates whether case $j$ was cited at the time case $i$ was introduced into the network. Just as for the outstar statistic, we include a weighting factor to favor more recent cases. \\[0.3cm]

@@

>>>>

Let $c_{ij} \in \{0,1\}$ be a binary indicator of whether case $i$ cites $j$. Furthermore, let
$$\mathcal{C}_t=\{c(t)\in \{0,1\}^{N_t}: c_{ij}(t)\in \{0,1\} \}$$ 
be the set of all possible citation combinations for opinions issued in term $t$, where $c_{ij}(t)$ is a binary indicator of whether case $i$ cites case $j$, and case $i$ is decided at time $t$. Note that the cardinality of $\mathcal{C}_t$ increases exponentially for every newly added case.\\ The probability function of the c-TERGM  is defined as
\begin{equation}
P_{\theta}(c(t)~|~c(t-))=\cfrac{\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}{\sum_{z(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(z(t)~|~c(t-)\big)\big)}
\label{ercm}
\end{equation}
where $c(t-)$ is a matrix that indicates the citations among cases decided before time $t$, $\theta \in \mathbb{R}^q$ is a $q$-dimensional vector of parameters,  $h: \mathcal{C}_t \to \mathbb{R}^q ~, ~ \c(t) \to (h_1(c(t)), \dots , h_q(c(t)))^T$ is a q-dimensional vector of different statistics and $\kappa(\theta) := \sum_{z(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(z(t)~|~c(t-)\big))$ is a normalization constant that ensures that Equation (\ref{ercm}) defines a probability function on $\mathcal{C}_t$.

% Network Statistics
The c-TERGM is specified through 
the decision regarding which network statistics $h(\cdot)$ to incorporate. We include the following statistics for the Supreme Court citation network, which are derived from the interdependence hypotheses described in the previous section:
$$h_{edges}:\mathcal{C}_t\to \mathbb{R}~~~, ~~~c(t) \to \sum_{i(t)} c_{ij}, $$
the number of citations made at time $t$, where $i(t)$ is the set of opinions issued at time $t$.  $h_{edges}$ performs the function of an intercept, and models the expected value of any given edge.
$$h_{outstar}:\mathcal{C}_t \to \mathbb{R}~~~, ~~~c(t) \to \sum_{i(t)} {\sum_{j \neq i} c_{ij} \choose 2} $$
the number of out-two-stars occuring at time $t$. An out-two-star is a configuration in which one node sends to two other nodes. The number of these configurations grows quadratically as the origins of ties concentrate on a few highly active/social senders. The out-two-stars configuration is commonly used to model sociality in ERGMs.
$$h_{instar}:\mathcal{C}_t \to \mathbb{R}~~~, ~~~c(t) \to \sum_{j(t)} {\sum_{i \neq j} c_{ij} \choose 2} $$
the number of in-two-stars occuring at time $t$. An in-two-star is a configuration in which one node receives ties from two other nodes. The number of these configurations grows quadratically as the destinations of ties concentrate on a few highly popular recipients. The out-two-stars configuration is commonly used to model popularity in ERGMs. [HERE]

$$h_{triangle}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{j<i}^Nc_i(t)\cdot c_j(t) \cdot
c_j(t_{-i}) \cdot w(a,b)$$
where $c_j(t_{-i})$ indicates whether case $j$ was cited at the time case $i$ was introduced into the network. Just as for the outstar statistic, we include a weighting factor to favor more recent cases. \\[0.3cm]

@@

% Network Statistics
The c-TERGM is specified through 
the decision regarding which network statistics $h(\cdot)$ to incorporate. We include the following statistics for the Supreme Court citation network:
$$h_{edges}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{i=1}^Nc_i(t)$$
the number of citations made at time $t$.  $h_{edges}$ is like an intercept, and models the expected value of any given edge.
$$h_{outstar}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{j<i}^Nc_i(t)\cdot c_j(t) \cdot \sqrt{\dfrac{(t-a)(t-a-b)}{t^2}}$$
the number of weighted outstars occuring at time $t$. We argue that it should be more likely to cite more recent cases than cases that have been decided further in the past. For the weight 
$$w(a,b):= \sqrt{\dfrac{(t-a)(t-a-b)}{t^2}}$$
we define $a$ and $b$ as the elapsed time since case $i$ and $j$ have been introduced to the network.
$$h_{triangle}:\mathcal{C}(N)\to \mathbb{R}~~~, ~~~c(t) \to \sum_{j<i}^Nc_i(t)\cdot c_j(t) \cdot
c_j(t_{-i}) \cdot w(a,b)$$
where $c_j(t_{-i})$ indicates whether case $j$ was cited at the time case $i$ was introduced into the network. Just as for the outstar statistic, we include a weighting factor to favor more recent cases. \\[0.3cm]
